Quantile Regressions via Method of Moments with multiple fixed effects \tnoteref{t1}

### 2023-11-13 article/article.tex
s
s

\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\makeatother
\journal{Journal Name}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{elsarticle-harv}
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Quantile Regressions via Method of Moments with multiple fixed effects},
  pdfauthor={Fernando Rios-Avila; Leonardo Siles; Gustavo Canavire-Bacarreza},
  pdfkeywords={Fixed effects, Linear heteroskedasticity, Location-scale
model, Quantile regression},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{frontmatter}
\title{Estimating Quantile Regressions with Multiple Fixed Effects through Method of Moments}
\fnref{fn1}

\author[1]{Fernando Rios-Avila%
\corref{cor1}%
}
 \ead{friosavi@levy.org}

\author[2]{Leonardo Siles%
%
}
 \ead{leonardosiles@hotmail.com} 
\author[3]{Gustavo Canavire-Bacarreza%
%
}
 \ead{gcanavire@worldbank.org}

@@

\fntext[fn1]{The opinions expressed in this paper are those of the
authors and do not necessarily reflect the views of the World Bank, its
Board of Directors, or the countries it represents.}

@@

\begin{keyword}
    Fixed Effects \sep Linear Heteroskedasticity \sep Location-Scale Model \sep Quantile Regression
\end{keyword}

\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, sharp corners, enhanced, breakable, frame hidden]}{\end{tcolorbox}}\fi

@@

Quantile regression (QR), introduced by \citet{koenkerbasset1978}, is an
estimation strategy used for modeling the relationships between
explanatory variables \(X\) and the conditional quantiles of the dependent
variable \(q_\tau (y|x)\). Using QR one can obtain richer
characterizations of the relationships between dependent and independent
variables by accounting for otherwise unobserved heterogeneity.

A relatively recent development in the literature has focused on
extending quantile regressions analysis to include individual fixed
effects in the framework of panel data. However, as described in
\citet{neymanscott1948} and \citet{lancaster2000}, when individual
fixed effects are included in quantile regression analysis an incidental parameter problem is generated. While many strategies have been
proposed for estimating this type of model (see
\citet{galvao2017quantile} for a brief review), neither has become
standard because of their restrictive assumptions in regard to the inclusion of 
individual and multiple fixed effects, the computational complexity, and implementation.

More recently, \citet{mss2019} (MSS hereafter) proposed a methodology
based on a conditional location-scale model, similar to the one described
in \citet{he1997} and \citet{zhao2000}, for the estimation of quantile
regressions models for panel data via a method of moments. This method
allows individual fixed effects to have heterogeneous effects
on the entire conditional distribution of the outcome, rather than
constraining their effect to be a location shift only, as in
\citet{canay2011}, \citet{koenker2004}, and \citet{lancaster2000}.

In principle, under the assumption that the data-generating process behind
the data is based on a multiplicative heteroskedastic process that is
linear in parameters \citep[\citet{mss2019}, \citet{he1997},
\citet{zhao2000}, \citet{cameron2005}], the effect of a variable \(X\) on the
\(q_{th}\) quantile can be derived as the combination of a location
effect and a scale effect moderated by the quantile of an underlying
independent and identically distributed (i.i.d.) error. For statistical inference, MSS derives the asymptotic distribution of the estimator, suggesting the use of bootstrap standard errors as well.

@@

In this framework, our paper expands on \citet{mss2019}, following some
of the suggestions by these authors regarding further research. First,
making use of the properties of generalized method of moments (GMM) estimators, we derive various
alternatives for the estimation of standard errors based on the
empirical influence functions of the estimators. Second, we reconsider
the application of Frisch-Waugh-Lovell (FWL) theorem
(\citet{frishwaugh1933} and \citet{lovell1963}) to extend the MSS
estimator to allow for the inclusion of multiple fixed effects, such as individual and year fixed effects.

@@

\hypertarget{sec-betas}{%
\subsection{Quantile Regression: Location-Scale Model}\label{sec-betas}}

Quantile regressions are used to identify relationships between the
explanatory variables \(X\) and the conditional quantiles of the
dependent variable \(Q(Y|\tau,X)\). This relationship is commonly
assumed to follow a linear functional form:

\begin{equation}\protect\hypertarget{eq-eq1}{}{q(Y|X,\tau) =X\beta(\tau)
}\label{eq-eq1}\end{equation}.

@@

\begin{equation}\protect\hypertarget{eq-eq2}{}{q(Y|X,\tau) =X\beta+X\gamma(\tau)
}\label{eq-eq2}\end{equation}.

Here, the location parameters \(\beta\) are typically identified using a
linear regression model (as in \citet{mss2019}) or a median regression
(as in \citet{melly2005}) and the scale parameters \(\gamma(\tau)\) can
be estimated using standard approaches.

@@

\begin{equation}\protect\hypertarget{eq-eq3}{}{\hat{\beta}(\tau) = \underset{\beta}{\operatorname{argmin}}
\left( \sum_{i\in y_i\geq x_i'\beta} \tau (y_i - x_i'\beta) - \sum_{i\in y_i<x_i'\beta} (1-\tau)(y_i - x_i'\beta) \right)
}\label{eq-eq3}\end{equation}.

@@

\begin{equation}\protect\hypertarget{eq-eq4}{}{\begin{aligned}
y_i &=x_i'\beta+\nu_i \\
\nu_i &=\varepsilon_i \times x_i'\gamma 
\end{aligned}
}\label{eq-eq4}\end{equation}.

@@

\begin{equation}\protect\hypertarget{eq-eq5}{}{q(Y|X,\tau) =X\beta+q(\varepsilon|\tau) \times X\gamma 
}\label{eq-eq5}\end{equation}.

In this setup, the traditional quantile coefficients are identified as
the location model coefficients plus the scale model coefficients
moderated by the \(\tau_{th}\) unconditional quantile of the
standardized error \(\varepsilon\).

\begin{equation}\protect\hypertarget{eq-eq6}{}{\beta(\tau) = \beta + q(\varepsilon|\tau) \times \gamma 
}\label{eq-eq6}\end{equation}.

While this specification imposes a strong assumption on the DGP, it has
two advantages over the standard quantile regression model. First,
because the location -scale model can be identified globally, with
only a single parameter (\(q(\varepsilon|\tau)\)) requiring local
estimation, this estimation approach will be more efficient than the
standard quantile regression model (\citet{zhao2000}). Second, under the
assumption that \(X\gamma\) is strictly positive, the model will
produce quantile coefficients that do not cross.

Following MSS, the quantile regression model defined by
Equation~\ref{eq-eq5} can be estimated using a generalized method of moments
approach. And while it is possible to identify all coefficients
(\(\beta,\gamma, q(\varepsilon|\tau)\)) simultaneously, we describe and
use the implementation approach advocated by MSS, which identifies each
set of coefficients separately.

First, the location model can be estimated using a standard linear
regression model where the dependent variable is the outcome \(Y\) and
the independent variables are the explanatory variables \(X\) (including
a constant) with an error \(u\), which is by definition heteroskedastic.
In this case, the location-model coefficients are identified under the
following condition:

\begin{equation}\protect\hypertarget{eq-eq7}{}{\begin{aligned}
      y_i &=x_i'\beta+\nu_i \\
      E\big[ x_i \nu_i\big] &=0
      \end{aligned}
}\label{eq-eq7}\end{equation}.

@@

\begin{equation}\protect\hypertarget{eq-eq8}{}{\begin{aligned}
  |\nu_i| &=x_i'\gamma+\omega_i \\
  E\big[ x_i \omega_i \big] &=0 \\
  E\big[ x_i (|\nu_i| -x_i'\gamma ) \big] &=0
  \end{aligned}
}\label{eq-eq8}\end{equation}.

@@

\begin{equation}\protect\hypertarget{eq-eq9}{}{\begin{aligned}
  E\left[  \mathbb{1}\left(x_i' (\beta + \gamma q(\varepsilon|\tau)) \geq y_i \right) - \tau \right] &=0  \\
  E\left[  \mathbb{1}\left(   q(\varepsilon|\tau)\geq \frac{y_i-x_i'\beta}{x_i'\gamma} \right) - \tau \right] &=0  \\
  \end{aligned}
}\label{eq-eq9}\end{equation},

where one identifies the quantile of the error \(\varepsilon\) using
standardized errors \(\frac{y_i-x_i'\beta}{x_i'\gamma}\) or by finding
the values that identify the overall quantile coefficients
\(\beta(\tau)=\beta + \gamma q(\varepsilon|\tau)\). Afterwards, the
conditional quantile coefficients are simply defined as the combination
of the location and scale coefficients.

\hypertarget{sec-se}{%
\subsection{Standard Errors: GLS, Robust, and Clustered}\label{sec-se}}

As discussed in the previous section, the estimation of quantile
regression coefficients using the location-scale model with
heteroskedastic linear errors can be estimated using the following set
of moments, which fits within the GMM framework:

\begin{equation}\protect\hypertarget{eq-eq10}{}{\begin{aligned}
  E[x_i \nu_i  ] &= E[h_{1,i}]=0 \\
  E[x_i  (|\nu_i|-x_i \gamma) ] &=E[h_{2,i}]=0 \\
  E\left[  \mathbb{1}\left(   q(\varepsilon|\tau)\geq \frac{y_i-x_i'\beta}{x_i'\gamma} \right) - \tau \right] 
  &=E[h_{3,i}]=0 
  \end{aligned}
}\label{eq-eq10}\end{equation}

@@

Call \(\theta=[ \beta' \ \ \gamma' \ \ q(\varepsilon|\tau)' ]'\) the set
of coefficients that are identified by the moment conditions in
Equation~\ref{eq-eq10}, a just identified model, and the function
\(h_i\) is a vector function that stacks all the moments described in Equation~\ref{eq-eq10} at the individual level. Then
\(\hat\theta\) follows a normal distribution with mean \(\theta\) and
variance-covariance matrix \(V(\theta)\) that is estimated as

\[
\hat{V}(\hat\theta)=\frac{1}{N} 
\bar G(\hat\theta)^{-1} 
\left( \frac{1}{N} \sum_{i=1}^N h_i h_i'  \Big|_{\theta=\hat\theta} \right) 
\bar G(\hat\theta)^{-1} 
\],

@@

In this framework, the quantile regression coefficients, a combination
of the location-scale-quantile estimates, will follow a normal
distribution with mean \(\beta(\tau) = \beta+q(\varepsilon|\tau)\gamma\)
and variance-covariance matrix equal to

\[\hat{V}(\beta(\tau)) = \Xi \hat{V}(\hat\theta) \Xi'
\],

@@

\begin{equation}\protect\hypertarget{eq-eqqtile}{}{\Xi = [ I(k), \hat q(\varepsilon|\tau) \times I(k), \hat \gamma ]
}\label{eq-eqqtile}\end{equation},

@@

\begin{equation}\protect\hypertarget{eq-eqvcv}{}{\hat{V}(\theta) = \frac{1}{N^2} \sum_{i=1}^N \lambda_i(\theta) \lambda_i(\theta)'
}\label{eq-eqvcv}\end{equation},

where the influence functions are defined as

\[\lambda_i(\theta) = \bar G(\theta)^{-1} h_i(\theta)\].

@@

\begin{equation}\protect\hypertarget{eq-ifs}{}{\begin{aligned}
\lambda_i(\theta)&=
  \begin{bmatrix}
  \lambda_{i}(\beta) \\
  \lambda_{i}(\gamma) \\
  \lambda_{i}(q(\varepsilon|\tau)) 
  \end{bmatrix} \\
\lambda_{i}(\beta)&=N (X'X)^{-1}  x_i ( x_i'\gamma) \times \varepsilon_i \\
\lambda_{i}(\gamma)&= N(X'X)^{-1} x_i ( x_i' \gamma ) \times (\tilde \varepsilon_i -1\big)\\
\lambda_{i}(q(\varepsilon|\tau))&=\frac{\tau-\mathbb{1}\big( q(\varepsilon|\tau)  \geq \varepsilon_i  \big) }{f_{\varepsilon}(q(\varepsilon|\tau))}
- \frac{ x_i'\gamma \times \varepsilon_i }{\bar x_i'\gamma} 
-  q(\varepsilon|\tau) \frac{  x_i' \gamma  \times (\tilde \varepsilon_i -1\big)}{\bar x_i'\gamma}
\end{aligned}
}\label{eq-ifs}\end{equation}.

@@

\[\hat{V}_{robust}
  \begin{pmatrix}
  \hat\beta \\
  \hat\gamma \\
  \hat q(\varepsilon|\tau)
  \end{pmatrix}
 = \frac{1}{N^2} 
 \begin{pmatrix}
 \sum \lambda_i(\beta) \lambda_i(\beta)' & \sum \lambda_i(\beta) \lambda_i(\gamma)' & \sum \lambda_i(\beta) \lambda_i(q(\varepsilon|\tau))' \\
 \sum \lambda_i(\gamma) \lambda_i(\beta)' & \sum \lambda_i(\gamma) \lambda_i(\gamma)' & \sum \lambda_i(\gamma) \lambda_i(q(\varepsilon|\tau))' \\
 \sum \lambda_i(q(\varepsilon|\tau) \lambda_i(\beta)' & \sum \lambda_i(q(\varepsilon|\tau))\lambda_i(\gamma)' & \sum \lambda_i(q(\varepsilon|\tau)) \lambda_i(q(\varepsilon|\tau))' 
  \end{pmatrix}
\].

@@

Let \(N_G\) be the total number of clusters $g$, where
\(g=1\dots N_G\). The clustered variance covariance matrix is given
by\footnote{It should be noted that one could just as well apply the
  insights of \citet{cameron_robust_2011}, allowing for multiway
  clustering.}

\[\hat{V}_{clustered}
  \begin{pmatrix}
  \hat\beta \\
  \hat\gamma \\
  \hat q(\varepsilon|\tau)
  \end{pmatrix}
 = \frac{1}{N^2} 
 \begin{pmatrix}
 \sum_{g=1}^{N_G} S\lambda_i(\theta) S\lambda_i(\theta)'
  \end{pmatrix}
\],

@@

The standard errors proposed by MSS can be understood as an application
of GLS, which will be valid as long as the
model for heteroskedasticity is correctly specified.\footnote{As
  discussed in most econometric textbooks, for example \citet{cameron2005}, one
  approach to correct for heteroskedasticity, when the
  heteroskedasticity functional form is known or can be estimated, is
  to use weighted least squares. While feasible, this approach
  would defeat the purpose of identifying quantile effects exploiting
  the heteroskedasticity of the model.} To estimate the GLS standard
errors, we make use of the following property:

@@

\[\begin{aligned}
\hat V(\hat \beta) &= \frac{1}{N} \sum_i^N \lambda_{i}(\beta) \lambda_{i}(\beta)' \\
&= \frac{1}{N}  (X'X)^{-1}  \sum_i^N x_i x_i' ( x_i'\gamma \times \varepsilon_i)^2 (X'X)^{-1} \\
\end{aligned}
\].

@@

\[\begin{aligned}
\hat V(\hat \beta) &= \frac{1}{N} \sum_i^N \lambda_{i}(\beta) \lambda_{i}(\beta)' \\
&= E(\varepsilon_i^2) \frac{1}{N}  (X'X)^{-1}  \sum_i^N x_i x_i' ( x_i'\gamma)^2 (X'X)^{-1} \\
&= \sigma^2_{\varepsilon} \frac{1}{N}  (X'X)^{-1}  \hat\Omega_{\beta\beta} (X'X)^{-1}  
\end{aligned}
\].

@@

\[\begin{aligned}
\hat\Omega_{ij} &= \frac{1}{N} \sum_i^N \tilde \lambda_{i}(\theta) \tilde \lambda_{j}(\theta)' \\
\hat\sigma_{ij} &= \frac{1}{N} \sum_i^N \phi_{i} \phi_{j}
\end{aligned}
\].

This estimator of standard errors is equivalent to the one derived by
MSS using Theorem 3.

@@

\[\begin{aligned}
w_{i} &= \delta_{g1}^w + \delta_{g2}^w + u_{i}^w \\
w_{i}^{rc} &= E(w_{i}) + \hat{u}_{i}^w
\end{aligned}
\].

>>>>

\tnotetext[t1]{The opinions expressed in this paper are those of the authors and do not necessarily reflect the views of the World Bank, its Board of Directors, or the countries it represents.}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{elsarticle-harv}
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Quantile Regressions via Method of Moments with multiple fixed effects },
  pdfauthor={Fernando Rios-Avila; Leonardo Siles; Gustavo Canavire-Bacarreza},
  pdfkeywords={Fixed effects, Linear heteroskedasticity, Location-scale
model, Quantile regression},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{frontmatter}
\title{Quantile Regressions via Method of Moments with multiple fixed
effects \tnoteref{t1}}
\author[1]{Fernando Rios-Avila%
\corref{cor1}%
}
 \ead{friosavi@levy.org} 
\author[2]{Leonardo Siles%
%
}
 \ead{leonardosiles@hotmail.com} 
\author[3]{Gustavo Canavire-Bacarreza%
%
}
 \ead{gcanavire@worldbank.org}

@@

@@

\begin{keyword}
    Fixed effects \sep Linear heteroskedasticity \sep Location-scale
model \sep 
    Quantile regression
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, breakable, frame hidden, interior hidden, enhanced, boxrule=0pt, sharp corners]}{\end{tcolorbox}}\fi

@@

Quantile regression (QR), introduced by \citet{koenkerbasset1978}, is an
estimation strategy used for modeling the relationships between
explanatory variables X and the conditional quantiles of the dependent
variable \(Q_y (\tau|x)\). Using QR one can obtain richer
characterizations of the relationships between dependent and independent
variables, by accounting for otherwise unobserved heterogeneity.

A relatively recent development in the literature has focused on
extending quantile regressions analysis to include individual fixed
effects in the framework of panel data. However, as described in
\citet{neymanscott1948}, and \citet{lancaster2000}, when individual
fixed effects are included in quantile regression analysis an incidental
parameter problem is generated. While many strategies have been proposed
for estimating this type of model (see \citet{galvao2017quantile} for a
brief review), neither has become standard because of their restrictive
assumptions in regard to the inclusion of individual and multiple fixed
effects, the computational complexity, and implementation.

More recently, \citet{mss2019} (MSS hereafter) proposed a methodology
based on a conditional location-scale model, similar to the one
described in \citet{he1997} and \citet{zhao2000}, for the estimation of
quantile regressions models for panel data via a method of moments. This
method allows individual fixed effects to have heterogeneous effects on
the entire conditional distribution of the outcome, rather than
constraining their effect to be a location shift only, as in
\citet{canay2011}, \citet{koenker2004}, and \citet{lamarche2010}.

In principle, under the assumption that data-generating process behind
the data is based on a multiplicative heteroskedastic process that is
linear in parameters \citep[\citet{he1997}, \citet{zhao2000},
\citet{cameron2005}]{mss2019}, the effect of a variable \(X\) on the
\(q_{th}\) quantile can be derived as the combination of a location
effect, and scale effect moderated by the quantile of an underlying
i.i.d. error. For statistical inference, MSS derives the asymptotic
distribution of the estimator, suggesting the use of bootstrap standard
errors, as well.

@@

In this framework, our paper expands on \citet{mss2019}, following some
of the suggestions by these authors regarding further research. First,
making use of the properties of generalized method of moments (GMM)
estimators, we derive various alternatives for the estimation of
standard errors based on the empirical influence functions of the
estimators. Second, we reconsider the application of Frisch-Waugh-Lovell
(FWL) theorem \citep[ and \citet{lovell1963}]{frishwaugh1933} to extend
the MSS estimator to allow for the inclusion of multiple fixed effects,
for example, individual and year fixed effects.

@@

\hypertarget{sec-betas}{%
\subsection{Quantile Regression: Location-Scale model}\label{sec-betas}}

Quantile regressions are used to identify relationships between the
explanatory variables \(X\) and the conditional quantiles of the
dependent variable \(Q_y(\tau|X)\). This relationship is commonly
assumed to follow a linear functional form:

\begin{equation}\protect\hypertarget{eq-eq1}{}{Q_y(\tau|X) =X\beta(\tau)
}\label{eq-eq1}\end{equation}

@@

\begin{equation}\protect\hypertarget{eq-eq2}{}{Q_y(\tau|X) =X\beta+X\gamma(\tau)
}\label{eq-eq2}\end{equation}

Here, the location parameters \(\beta\) are typically identified using a
linear regression model (as in \citet{mss2019}) or a median regression
(as in \citet{zhao2000}) and the scale parameters \(\gamma(\tau)\) can
be estimated using standard approaches.

@@

\begin{equation}\protect\hypertarget{eq-eq3}{}{\hat{\beta}(\tau) = \underset{\beta}{\operatorname{argmin}}
\left( \sum_{i\in y_i\geq x_i'\beta} \tau (y_i - x_i'\beta) - \sum_{i\in y_i<x_i'\beta} (1-\tau)(y_i - x_i'\beta) \right)
}\label{eq-eq3}\end{equation}

@@

\begin{equation}\protect\hypertarget{eq-eq4}{}{\begin{aligned}
y_i &=x_i'\beta+\nu_i \\
\nu_i &=\varepsilon_i \times x_i'\gamma 
\end{aligned}
}\label{eq-eq4}\end{equation}

@@

\begin{equation}\protect\hypertarget{eq-eq5}{}{Q_y(\tau|X) =X\beta+Q_\varepsilon(\tau) \times X\gamma 
}\label{eq-eq5}\end{equation}

In this setup, the traditional quantile coefficients are identified as
the location model coefficients plus the scale model coefficients
moderated by the \(\tau_{th}\) unconditional quantile of the
standardized error \(\varepsilon\). For simplicity we will use
\(q(\tau)\) to denote \(Q_\varepsilon(\tau)\) in the rest of the paper.

\begin{equation}\protect\hypertarget{eq-eq6}{}{\beta(\tau) = \beta + q(\tau) \times \gamma 
}\label{eq-eq6}\end{equation}

While this specification imposes a strong assumption on the DGP, it has
two advantages over the standard quantile regression model. First,
because the location-scale model can be identified globally, with only a
single parameter (\(q(\tau)\)) requiring local estimation, this
estimation approach will be more efficient than the standard quantile
regression model (\citet{zhao2000}). Second, under the assumption that
\(X\gamma\) is strictly positive, the model will produce quantile
coefficients that do not cross.

Following MSS, the quantile regression model defined by
Equation~\ref{eq-eq5} can be estimated using a generalized method of
moments approach. And while it is possible to identify all coefficients
(\(\beta,\gamma, q(\tau)\)) simultaneously, we describe and use the
implementation approach advocated by MSS, which identifies each set of
coefficients separately.

First, the location model can be estimated using a standard linear
regression model, where the dependent variable is the outcome \(Y\) and
the independent variables are the explanatory variables \(X\) (including
a constant) with an error \(u\), which is by definition heteroskedastic.
In this case, the location-model coefficients are identified under the
following condition:

\begin{equation}\protect\hypertarget{eq-eq7}{}{\begin{aligned}
      y_i &=x_i'\beta+\nu_i \\
      E\big[ x_i \nu_i\big] &=0
      \end{aligned}
}\label{eq-eq7}\end{equation}

@@

\begin{equation}\protect\hypertarget{eq-eq8}{}{\begin{aligned}
  |\nu_i| &=x_i'\gamma+\omega_i \\
   E\big[ x_i (|\nu_i| -x_i'\gamma ) \big] &=0
  \end{aligned}
}\label{eq-eq8}\end{equation}

@@

\begin{equation}\protect\hypertarget{eq-eq9}{}{\begin{aligned}
  E\left[  \mathbb{1}\left(x_i' (\beta +   \gamma q(\tau)) \geq y_i \right) - \tau \right] &=0  \\
  E\left[  \mathbb{1}\left(   q(\tau) \geq \frac{y_i-x_i'\beta}{x_i'\gamma} \right) - \tau \right] &=0  \\
  \end{aligned}
}\label{eq-eq9}\end{equation}

where one identifies the quantile of the error \(\varepsilon\) using
standardized errors \(\frac{y_i-x_i'\beta}{x_i'\gamma}\) or by finding
the values that identify the overall quantile coefficients
\(\beta(\tau)=\beta + \gamma q(\tau)\). Afterwards, the conditional
quantile coefficients are simply defined as the combination of the
location and scale coefficients.

\hypertarget{sec-se}{%
\subsection{Standard Errors: GLS, Robust, Clustered}\label{sec-se}}

As discussed in the previous section, the estimation of quantile
regression coefficients using the location-scale model with
heteroskedastic linear errors can be estimated using a the following set
of moments, which fits within the GMM framework:

\begin{equation}\protect\hypertarget{eq-eq10}{}{\begin{aligned}
  E[x_i \nu_i  ] &= E[h_{1,i}]=0 \\
  E[x_i  (|\nu_i|-x_i \gamma) ] &=E[h_{2,i}]=0 \\
  E\left[  \mathbb{1}\left(   q(\tau)\geq \frac{y_i-x_i'\beta}{x_i'\gamma} \right) - \tau \right] 
  &=E[h_{3,i}]=0 
  \end{aligned}
}\label{eq-eq10}\end{equation}

@@

Call \(\theta=[ \beta' \ \ \gamma' \ \ q(\tau) ]'\) the set of
coefficients that are identified by the moment conditions in
Equation~\ref{eq-eq10}, a just identified model, and the function
\(h_i\) is a vector function that stacks all the moments described in
Equation~\ref{eq-eq10} at the individual level. Then \(\hat\theta\)
follows a normal distribution with mean \(\theta\) and
variance-covariance matrix \(V(\theta)\) that is estimated as

\[
\hat{V}(\hat\theta)=\frac{1}{N} 
\bar G(\hat\theta)^{-1} 
\left( \frac{1}{N} \sum_{i=1}^N h_i h_i'  \Big|_{\theta=\hat\theta} \right) 
\bar G(\hat\theta)^{-1} 
\]

@@

In this framework, the quantile regression coefficients, a combination
of the location-scale-quantile estimates, will follow a normal
distribution with mean
\(\beta(\tau) = \beta+\gamma q(\varepsilon | \tau)\) and
variance-covariance matrix equal to

\[\hat{V}(\beta(\tau)) = \Xi \hat{V}(\hat\theta) \Xi'
\]

@@

\begin{equation}\protect\hypertarget{eq-eqqtile}{}{\Xi = [ I(k), \hat q(\tau) \times I(k), \hat \gamma ]
}\label{eq-eqqtile}\end{equation}

@@

\begin{equation}\protect\hypertarget{eq-eqvcv}{}{\hat{V}(\theta) = \frac{1}{N^2} \sum_{i=1}^N \lambda_i(\theta) \lambda_i(\theta)'
}\label{eq-eqvcv}\end{equation}

where the influence functions are defined as:

\[\lambda_i(\theta) = \bar G(\theta)^{-1} h_i(\theta)\]

@@

\begin{equation}\protect\hypertarget{eq-ifs}{}{\begin{aligned}
\lambda_i(\theta)&=
  \begin{bmatrix}
  \lambda_{i}(\beta) \\
  \lambda_{i}(\gamma) \\
  \lambda_{i}(q(\tau)) 
  \end{bmatrix} \\
\lambda_{i}(\beta)&=N (X'X)^{-1}  x_i ( x_i'\gamma) \times \varepsilon_i \\
\lambda_{i}(\gamma)&= N(X'X)^{-1} x_i ( x_i' \gamma ) \times (\tilde \varepsilon_i -1\big)\\
\lambda_{i}(q(\tau))&=\frac{\tau-\mathbb{1}\big( q(\tau)  \geq \varepsilon_i  \big) }{f_{\varepsilon}(q(\tau))}
- \frac{ x_i'\gamma \times \varepsilon_i }{\bar x_i'\gamma} 
-  q(\tau) \frac{  x_i' \gamma  \times (\tilde \varepsilon_i -1\big)}{\bar x_i'\gamma}
\end{aligned}
}\label{eq-ifs}\end{equation}

@@

\[\hat{V}_{robust}
  \begin{pmatrix}
  \hat\beta \\
  \hat\gamma \\
  \hat q(\tau)
  \end{pmatrix}
 = \frac{1}{N^2} 
 \begin{pmatrix}
 \sum \lambda_i(\beta) \lambda_i(\beta)' & \sum \lambda_i(\beta) \lambda_i(\gamma)' & \sum \lambda_i(\beta) \lambda_i(q(\tau))' \\
 \sum \lambda_i(\gamma) \lambda_i(\beta)' & \sum \lambda_i(\gamma) \lambda_i(\gamma)' & \sum \lambda_i(\gamma) \lambda_i(q(\tau))' \\
 \sum \lambda_i(q(\tau)) \lambda_i(\beta)' & \sum \lambda_i(q(\tau))\lambda_i(\gamma)' & \sum \lambda_i(q(\tau)) \lambda_i(q(\tau))' 
  \end{pmatrix}
\]

@@

Let \(N_G\) be the total number of clusters \(g\), where
\(g=1\dots N_G\). The clustered variance covariance matrix is given
by\footnote{It should be noted that one could just as well apply the
  insights of \citet{cameron_robust_2011}, allowing for multiway
  clustering.}

\[\hat{V}_{clustered}
  \begin{pmatrix}
  \hat\beta \\
  \hat\gamma \\
  \hat q(\tau)
  \end{pmatrix}
 = \frac{1}{N^2} 
 \begin{pmatrix}
 \sum_{g=1}^{N_G} S\lambda_i(\theta) S\lambda_i(\theta)'
  \end{pmatrix}
\]

@@

The standard errors proposed by MSS can be understood as an application
of GLS, which will be valid as long as the model for heteroskedasticity
is correctly specified.\footnote{As discussed in most econometric
  textbooks, for example \citet{cameron2005}, one approach to correct
  for heteroskedasticity, when the heteroskedasticity functional form is
  known or can be estimated, is to use weighted least squares. While
  feasible this approach would defeat the purpose of identifying
  quantile effects exploiting the heteroskedasticity of the model.} To
estimate the GLS standard errors, we make use of the following property:

@@

\[\begin{aligned}
\hat V(\hat \beta) &= \frac{1}{N} \sum_i^N \lambda_{i}(\beta) \lambda_{i}(\beta)' \\
&= \frac{1}{N}  (X'X)^{-1}  \sum_i^N x_i x_i' ( x_i'\gamma \times \varepsilon_i)^2 (X'X)^{-1} \\
\end{aligned}
\]

@@

\[\begin{aligned}
\hat V(\hat \beta) &= \frac{1}{N} \sum_i^N \lambda_{i}(\beta) \lambda_{i}(\beta)' \\
&= E(\varepsilon_i^2) \frac{1}{N}  (X'X)^{-1}  \sum_i^N x_i x_i' ( x_i'\gamma)^2 (X'X)^{-1} \\
&= \sigma^2_{\varepsilon} \frac{1}{N}  (X'X)^{-1}  \hat\Omega_{\beta\beta} (X'X)^{-1}  
\end{aligned}
\]

@@

\[\begin{aligned}
\hat\Omega_{jk} &= \frac{1}{N} \sum_{i=1}^N \tilde \lambda_{i,j}(\theta) \tilde \lambda_{i,k}(\theta)' \\
\hat\sigma_{jk} &= \frac{1}{N} \sum_{i=1}^N \psi_{i,j} \psi_{i,k}
\end{aligned}
\]

This estimator of stand ard errors is equivalent to the one derived by
MSS using Theorem 3.

@@

\[\begin{aligned}
w_{i} &= \delta_{g1}^w + \delta_{g2}^w + u_{i}^w \\
w_{i}^{rc} &= E(w_{i}) + \hat{u}_{i}^w
\end{aligned}
\]
